---
title: "clipper"
output:
  rmarkdown::html_vignette:
    self_contained: no

  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r opts, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = TRUE,
  message = TRUE,
  width = 120,
  comment = "#>",
  fig.retina = 2,
  fig.path = "README-"
)
```

[![Build Status](https://travis-ci.org/hypertidy/clipper.svg)](https://travis-ci.org/hypertidy/clipper) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/hypertidy/clipper?branch=master&svg=true)](https://ci.appveyor.com/project/hypertidy/clipper)
[![codecov](https://codecov.io/gh/hypertidy/clipper/branch/master/graph/badge.svg)](https://codecov.io/gh/hypertidy/clipper)
[![Project Status: Concept](http://www.repostatus.org/badges/latest/concept.svg)](http://www.repostatus.org/#concept)

# clipper: Another Port of Angus Johnson's ['clipper' Polygon Clipping Library](http://angusj.com/delphi/clipper.php)

A few scribbles extending beyond CRAN package
[`polyclip`](https://cran.r-project.org/package=polyclip)
to use `clipper` for a few commonly used manipulations. Package has two sets of
internal data to play with:

1. `castlemaine` - An `SC` representation of the street network of Castlemaine,
   Australia.
2. `castlemaine_green` - An `sf::sfc` object containing all the polygons of
   green areas (parks, paddocks, lawns, forests) in eponymous location.

## Lengths of Paths throught Polygons

The `castlemaine` data set can be used to generate paths via `dodgr`, and the
currently sole demo function can then take the polygon layer and determine the
relative length of the path that passes through the polygons. Preliminary
pre-processing, creating the `dodgr` street network, and extracting the
vertices to be used to generate a random path.

```{r streetnet}
devtools::load_all (".", export_all = FALSE)
streetnet <- dodgr::weight_streetnet (castlemaine, wt_profile = "foot")
v <- dodgr::dodgr_vertices (streetnet)
v0 <- sample (v$id, size = 1)
v1 <- sample (v$id, size = 1)
p <- dodgr::dodgr_paths (streetnet, from = v0, to = v1)
p <- v [match (p [[1]] [[1]], v$id), ]
head (p)
```
We then just need to extract the coordinates of the polygon layer, and ensure
that the columns are labelled `x` and `y`:
```{r green}
green_polys <- castlemaine_green
green <- lapply (green_polys$geometry, function (i) {
                     res <- i [[1]]
                     colnames (res) <- c ("x", "y")
                     return (res)   })
length (green)
head (green [[1]])
```
Then we're good to go ...
```{r path_through_poly}
path_through_poly (p, green)
```
And `r formatC (path_through_poly (g, green) * 100, format = "f", digits = 1)`%
of that path passes through the green polygons.
